Variational oblique predictive clustering trees

### 2025-02-06 reports/paper/vspyct.tex
fix in the STR table - OPCT best score on cpmp

\begin{table}[h!]
\centering
\caption{\textit{MAE} scores for STR (lowest is best)}
\label{tab:str_results}
\begin{tabular}{@{}lccccc@{}}
\toprule
Dataset & SPYCT-single & SPYCT-ensemble & VSPYCT & PCT-Ensemble & OPCT \\ \midrule
era                             & 1.296625 & \textbf{1.249352} & 1.287840 & 1.277622 & 1.277424 \\
cpmp2015                        & 1137.738259 & 997.261786 & \textbf{918.481147} & 1211.124409 & 848.721320 \\
qsar234                         & 0.572577 & \textbf{0.415656} & 0.428724 & 0.428721 & 0.441020 \\
puma8NH                         & 2.795463 & \textbf{2.632242} & 2.711678 & - & - \\
yprop                           & 0.020126 & 0.019693 & 0.019969 & \textbf{0.019682} & 0.023687 \\
space\_ga                       & 0.105716 & 0.090193 & 0.104501 & \textbf{0.084793} & 0.099387 \\
bike\_sharing                   & 7.866288 & 3.101784 & 11.288880 & 10.610927 & \textbf{2.509829} \\
quake                           & 0.144549 & 0.143972 & \textbf{0.143805} & 0.147743 & 0.172350 \\
concrete\_compressive\_strength & 4.500918 & \textbf{4.121670} & 7.740371 & 4.164038 & 4.216046 \\
ailerons                        & 0.000135 & \textbf{0.000124} & 0.000127 & 0.000133 & 0.000161 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{\textit{MAE} scores for STR (lowest is best)}
\label{tab:str_results}
\begin{tabular}{@{}lccccc@{}}
\toprule
Dataset & SPYCT-single & SPYCT-ensemble & VSPYCT & PCT-Ensemble & OPCT \\ \midrule
era                             & 1.296625 & \textbf{1.249352} & 1.287840 & 1.277622 & 1.277424 \\
cpmp2015                        & 1137.738259 & 997.261786 & 918.481147 & 1211.124409 & \textbf{848.721320} \\
qsar234                         & 0.572577 & \textbf{0.415656} & 0.428724 & 0.428721 & 0.441020 \\
puma8NH                         & 2.795463 & \textbf{2.632242} & 2.711678 & - & - \\
yprop                           & 0.020126 & 0.019693 & 0.019969 & \textbf{0.019682} & 0.023687 \\
space\_ga                       & 0.105716 & 0.090193 & 0.104501 & \textbf{0.084793} & 0.099387 \\
bike\_sharing                   & 7.866288 & 3.101784 & 11.288880 & 10.610927 & \textbf{2.509829} \\
quake                           & 0.144549 & 0.143972 & \textbf{0.143805} & 0.147743 & 0.172350 \\
concrete\_compressive\_strength & 4.500918 & \textbf{4.121670} & 7.740371 & 4.164038 & 4.216046 \\
ailerons                        & 0.000135 & \textbf{0.000124} & 0.000127 & 0.000133 & 0.000161 \\
\bottomrule
\end{tabular}
\end{table}
